Bayesian Neural Networks

### 2024-04-16 Paper/paper.tex
Updated models and paper

\documentclass[12pt]{article}
\usepackage{fancyhdr}     % Enhanced control over headers and footers 
\usepackage[T1]{fontenc}  % Font encoding
\usepackage{mathptmx}     % Choose Times font 
\usepackage{microtype}    % Improves line breaks      
\usepackage{setspace}     % Makes the document look like horse manure 
\usepackage{hyperref}
\hypersetup{
	colorlinks   = true, %Colours links instead of ugly boxes
	urlcolor     = blue, %Colour for external hyperlinks
	linkcolor    = black, %Colour of internal links
	citecolor   = black %Colour of citations
}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{endnotes}
\usepackage{float}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{multicol}
\usepackage{tikz}
\usetikzlibrary{snakes}
\usepackage{rotating}
\usetikzlibrary{positioning,shapes.multipart}

@@

A neural network takes a series of inputs... In figure \ref{fig:example-nn}, the network takes two inputs, has one hidden layer of size

@@

 ...

@@

Bayesian neural networks take the same principle as

Similar to a Neural network such as...

@@

@@

The CIFAR-10 ((Canadian Institute For Advanced Research 10) dataset is a machine learning benchmarking set. It contatins 60,000 $16 \times 16$ RGB pictures of: airplanes, cars, birds, cats, deer, dogs, frogs, horses, ships, and trucks\cite{cifar10}. It is used...

@@

We used the following hyperparamaters for training:
\begin{figure}[H]
	\begin{center}
	\begin{tabular}{|c||p{3cm}|p{3cm}|} % Adjust p{width} as needed
		\hline
		\textbf{Hyperparameter} & \textbf{CNN} & \textbf{BCNN} \\ [0.5ex] 
		\hline\hline
		Epochs & 500 & 500\\
		\hline
		Learning Rate & ....  & May be higher (0.01 - 0.1) due to simpler structure  \\
		\hline
		Regularization & L1/L2 weight decay or Dropout common to prevent overfitting & Can benefit from Dropout, but weight decay might be less crucial \\
		\hline
		Optimizer & Adamw  & Adamw  \\
		\hline
	\end{tabular}
\end{center}
\end{figure}

In addition to the above, the two models have the same number of levels...

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{../Images/CNN_confusion_matrix}
		\caption{CNN}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{../Images/BNN_confusion_matrix}
		\caption{BCNN}
	\end{subfigure}
	\caption{Confusion matrices}
\end{figure}

The two have roughly similar accuracies given the model

>>>>

\documentclass[12pt]{article}
\usepackage{fancyhdr}     % Enhanced control over headers and footers 
\usepackage[T1]{fontenc}  % Font encoding
\usepackage{mathptmx}     % Choose Times font 
\usepackage{microtype}    % Improves line breaks      
\usepackage{setspace}     % Makes the document look like horse manure 
\usepackage{hyperref}
\hypersetup{
	colorlinks   = true, %Colours links instead of ugly boxes
	urlcolor     = blue, %Colour for external hyperlinks
	linkcolor    = black, %Colour of internal links
	citecolor   = black %Colour of citations
}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{endnotes}
\usepackage{float}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{multicol}
\usepackage{tikz}
\usetikzlibrary{snakes}
\usepackage{rotating}
\usetikzlibrary{positioning,shapes.multipart}
 \usepackage{listings}

@@

A neural network takes a series of inputs. An example of a neural network with two inputs, one hidden layer of size three, and two outputs appears in figure \ref{fig:example-nn}

\subsection{Neural Network Neurons}

@@

@@

Bayesian neural networks operate the same way as a normal

\subsection{Bayesian Neural Network Neuron}

Similar to a neural network such as...

@@

\subsubsection{Priors}

This section was requested by Micheal.

@@

The CIFAR-10 ((Canadian Institute For Advanced Research 10) dataset is a popular machine learning  dataset set. It contatins 60,000 $16 \times 16$ color pictures of: airplanes, cars, birds, cats, deer, dogs, frogs, horses, ships, and trucks\cite{cifar10}. Because of its simple task and variety of images, it is often used as a baseline task for new  model structures.

@@

We used the following hyperparamaters for training:
\begin{figure}[H]
	\begin{center}
	\begin{tabular}{|c||p{3cm}|p{3cm}|} % Adjust p{width} as needed
	\hline
	\textbf{Hyperparameter} & \textbf{CNN} & \textbf{BCNN} \\ [0.5ex] 
	\hline\hline
	Epochs & 100 & 100\\
	\hline
	Learning Rate & 0.001  & 0.003  \\
	\hline
	Regularization Rate& 0.001 & 0.001 \\
	\hline
	Optimizer & Adamw  & Adamw  \\
	\hline
\end{tabular}
\end{center}
\end{figure}

In addition to the hyperparamaters above, the two models have the same number of layers and levels. We did not adjust the priors, as those were set by the BCNN layer code from \cite{shridhar2018uncertainty}.

@@

\begin{figure}[H]
	\begin{tabular}{|c||p{3cm}|p{3cm}|} % Adjust p{width} as needed
		\hline
		\textbf{Metric} & \textbf{CNN} & \textbf{BCNN} \\ [0.5ex] 
		\hline\hline
		Train Accuracy & 84.96\% & 81.27\%\\
		\hline
		Validation Accuracy & 61.76\%  & 59.21\%  \\
		\hline
		Time to Train & 16 min 11 sec  & 22 min 11 sec  \\
		\hline
	\end{tabular}
\end{figure}

The results we achieved with training were about the same between the BCNN and the CNN. However, the bayesian model took longer to train.

\begin{figure}[H]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../Images/CNN_val_acc_over_time}
		\caption{CNN}
	\end{subfigure}% //  
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../Images/BNN_val_acc_over_time}
		\caption{BCNN}
	\end{subfigure}
	\caption{Train vs validation accuracy over time}
	\label{fig:train-v-val}
\end{figure}

Additionally, neither model converged with the train and validation accuracy, this is an indication that we might need to increase the regularization rate. Another thing to note from figure \ref{fig:train-v-val} is that the BCNN took longer to divirge from the train accuracy.

\begin{figure}[H]
	\centering
	\begin{subfigure}{\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{../Images/CNN_confusion_matrix}
		\caption{CNN}
	\end{subfigure} \\% //  
	\begin{subfigure}{\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{../Images/BNN_confusion_matrix}
		\caption{BCNN}
	\end{subfigure}
	\caption{Confusion matrices}
\end{figure}

The two models have the same set of confusions
